The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-10-25 paper/ms.tex
turn off hyperref for the moment

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{xspace}
\usepackage{hyperref}

@@

% Abstract of the paper
\begin{abstract}
Here we present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained by \kepler to reconstruct light curves of 102~stars too bright to have been otherwise targeted. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission. In this Paper, we focus in particular on a subset of these consisting of 66~red giants for which we detect solar-like oscillations. Using high-resolution spectroscopy from the Tillinghast Reflector \'{E}chelle Spectrograph (TRES) together with asteroseismic modelling, we obtain the stellar densities and derive masses, radii and ages of~34 of these red giant and red clump stars as benchmarks. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
\end{abstract}

@@

Because the smear data are collected along an entire CCD~column, there is the risk of contamination from other bright stars. This is especially true in doing asteroseismology of red giants, where the low-amplitude stochastically-excited oscillations can be washed out in a power spectrum by the coherent high amplitude variations of a classical pulsator, even if the background star is much fainter. We can assess the importance of this contamination by considering the differences between odd and even quarters: because the \kepler spacecraft rotates $90^{\circ}$ between successive quarters, any contaminant will lie in the same column as a smear target only every second quarter, falling in the other quarters in the same row but not necessarily the same column. We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, clipped for outliers, and considering only odd and even quarters, and visually inspected these for significant differences. In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect. In the case of HD~181878, a red giant, there is clear and significant contamination from an M~giant, as is seen in Figure~\ref{contamination}. Likewise HD~183383 shows two different stars, depending on the quarter: some parts are likely from an ellipsoidal variable with a period of 6.46 days, other parts are from an RR Lyrae pulsator.

@@

@@

BP acknowledges being on the traditional territory of the Lenape Nations and, today, we recognize that Manhattan continues to be the home to many Algonkian peoples. We thank the Lenape peoples for allowing us to carry out this work on the Lenape original homelands at New York University. BP and TW would like to acknowledge the Gadigal people of the Eora Nation and the Norongerragal and Gweagal peoples of the Tharawal Nation as the traditional owners of the land at the University of Sydney and the Sutherland Shire on which some of this work was carried out, and pay their respects to their knowledge, and their elders past, present and future.

>>>>

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{xspace}

@@

% Abstract of the paper
\begin{abstract}
Here we present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained by \kepler to reconstruct light curves of 102~stars too bright to have been otherwise targeted. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission. In this Paper, we focus in particular on a subset of these consisting of 66~red giants for which we detect solar-like oscillations.y All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
\end{abstract}

@@

Because the smear data are collected along an entire CCD~column, there is the risk of contamination from other bright stars. This is especially true in doing asteroseismology of red giants, where the low-amplitude stochastically-excited oscillations can be washed out in a power spectrum by the coherent high amplitude variations of a classical pulsator, even if the background star is much fainter. We can assess the importance of this contamination by considering the differences between odd and even quarters: because the \kepler spacecraft rotates $90^{\circ}$ between successive quarters, any contaminant will lie in the same column as a smear target only every second quarter, falling in the other quarters in the same row but not necessarily the same column. We have therefore generated Lomb-Scargle periodograms \citep{lomb,scargle} of each light curve, clipped for outliers, and considering only odd and even quarters, and both visually inspected these for significant differences. In the great majority of cases they closely resemble one another, indicating that contamination is at worst a minor effect. In order to better quantify this, we compute the inner product of  normalized periodograms of the odd and even quarters each smoothed with a 3-element Gaussian kernel. If this overlap integral is 1, then the power spectra are identical; substantial departures from unity may be caused by real nonstationary or long-period stellar variation, noise, or gain or contamination differences between the seasons. We find that the distribution of overlaps is strongly peaked around $\sim 0.91$, with a tail of 22 stars showing overlap $< 0.9$. We investigate these further, finding that in not all of these cases is there an obvious problem, for example the classical pulsator HD~175841 in which amplitudes of several pulsations have changed but the overall distribution seems very similar, in which we conclude that the variation is probably astrophysical or an artefact of our data processing.

In the case of HD~181878, a red giant, there is clear and significant contamination from an M~giant, as is seen in Figure~\ref{contamination}. Likewise HD~183383 shows two different stars, depending on the quarter: some parts are likely from an ellipsoidal variable with a period of 6.46 days, other parts are from an RR Lyrae pulsator. Between seasons, there is an extra hump of power near the red giant oscillations in HD~175740; extra low frequency power in HD~180658; one coherent peak in  HD~182694; high frequency contamination in HD~181597 possibly from an EB; and a very significant difference in amplitude between seasons for BD~+39~3882. In other cases visual inspection does not show severe contamination, but in all cases we recommend that users of these light curves carefully check for differences between odd and even quarters.

@@

\begin{figure}
\noindent\includegraphics[width=8cm,keepaspectratio]{contam.eps}

\caption{\label{contamination2}
Histogram over overlap integrals of smoothed periodograms of odd and even quarters for each star in the sample. The peak at $\sim 0.91$ contains normal stars with limited contamination; we investigate the 22 stars with overlaps below 0.9 for which there is a significant risk of contamination.}
\end{figure}

@@

BP acknowledges being on the traditional territory of the Lenape Nations and recognizes that Manhattan continues to be the home to many Algonkian peoples. We give blessings and thanks to the Lenape people and Lenape Nations in recognition that we are carrying out this work on their indigenous homelands. We would like to acknowledge the Gadigal people of the Eora Nation and the Norongerragal and Gweagal peoples of the Tharawal Nation as the traditional owners of the land at the University of Sydney and the Sutherland Shire on which some of this work was carried out, and pay their respects to their knowledge, and their elders past, present and future.
